A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
remove readme figure

This command will create a file with the name `README.Rmd`.
<!--knit/rmarkdown will be explained in section above-->
When you knit this file, it, in turn, creates a `README.md`.
That means you can include R code or plots etc., within the readme.
The `README.md` file will look pleasant in the browser, just like in Figure \@ref(fig:readme).

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
if (!file.exists(readme)) {
  webshot2::webshot(
    "https://github.com/aaronpeikert/repro-tutorial/",
    file = readme,
    vwidth = 1920,
    # height & width are not resolution
    vheight = 1080,
    # but what website thinks the browser size is
    selector = "div#readme",
    zoom = 2
  ) # higher resolution
}
```

```{r readme, echo=FALSE, fig.cap="A screenshot of how a README.md is rendered/presented on GitHub.  ", out.width='100%'}
knitr::include_graphics(readme)
```

@@

Ideally, you have a statement in the README that contains a short description of how to reproduce the project, whereas most steps are automatic and standardized.
This statement should also list all software requirements.
<!--AP: I think this Figure is superfluous. Please remove. All the information is in the following code blocks.-->
Figure \@ref(fig:readme) shows `r link("https://github.com/aaronpeikert/repro-tutorial#how-to-reproduce-this-manuscript", "the reproduction statement of this project")`.
For example, you can download any git repository with these commands:

>>>>

This command will create a file with the name `README.Rmd`.
<!--knit/rmarkdown will be explained in section above-->
When you knit this file, it, in turn, creates a `README.md`.
That means you can include R code or plots etc., within the readme.
The `README.md` file will look pleasant in the browser on `r link("https://github.com/aaronpeikert/repro-tutorial#readme", "GitHub")`.

@@

Ideally, you have a statement in the README that contains a short description of how to reproduce the project, whereas most steps are automatic and standardized.
This statement should also list all software requirements.
For example, you can download any git repository with these commands:
